Adversarial Variational Optimization of\\ Non-Differentiable Simulators

### 2018-01-30 icml/avo.tex
save

Preliminary results on toy problems with discrete and continuous data validate
the proposed method. While the obtained results are encouraging, the complete
validation of the method remains to be carried out in real conditions on a full
fledged scientific simulator -- which we plan to achieve for a next version of
this work. In terms of method, several components need further investigation.
First, we need to better study the interplay between the entropic regularization and the
adversarial objectives. Second, we should better understand the dynamics of the
optimization procedure, in particular when combined with momentum-based
optimizers like Adam. Third, we need to consider whether less noisy estimates of
the gradients $\nabla_\bfpsi U_g$ can be computed.

>>>>

Preliminary results on toy problems with discrete and continuous data validate
the proposed method. While the obtained results are encouraging, the complete
validation of the method remains to be carried out in real conditions on a full
fledged scientific simulator -- which we plan to achieve for a next version of
this work \glnote{to update}. In terms of method, several components need further investigation.
First, we need to better study the interplay between the entropic regularization and the
adversarial objectives. Second, we should better understand the dynamics of the
optimization procedure, in particular when combined with momentum-based
optimizers like Adam. Third, we need to consider whether less noisy estimates of
the gradients $\nabla_\bfpsi U_g$ can be computed.
